\documentclass[nobib]{tufte-handout}
%\documentclass[11pt]{tufte-book}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{accents}
\usepackage{blindtext}
\usepackage{hyphenat}
\usepackage{comment}
\usepackage{complexity}
\usepackage{framed}
\usepackage{csquotes}
%s\usepackage[usenames, dvipsnames]{color}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem}
%\setlength\titlebox{6.5cm}    % You can expand the title box if you
% really have to

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\hyphenation{Efficient}
\hyphenation{Computation}

\title[Rationality and Efficient Verifiable Computation]{Rationality and Efficient Verifiable Computation\\ \noindent \small{Dissertation proposal}}


\author{Matteo Campanelli}
\date{}

\newtheorem{remark}{Remark}

\begin{document}
\maketitle

  
  \begin{abstract}
  	\noindent
  	We propose the study of protocols for delegating computation in a model in which one of the party is rational.
  	A \textit{delegator} outsources the computation of a function $f$ on input $x$ to a \textit{worker}, who
  	receives a (possibly monetary) reward. Our goal is to design \textit{very efficient} delegation schemes 
  	where a worker is economically incentivized to provide the correct result
  	$f(x)$. As a design choice, we do not want to rely on cryptographic assumptions
  	(i.e. we will not assume one-way functions exist).
  	
  	We provide several results within the framework of rational proofs introduced by Azar and Micali (STOC 2012).
  	We make several contributions to efficient rational proofs for general feasible computations.
  	First, we design schemes with a sublinear verifier with low round and communication complexity for
  	space-bounded computations.
  	Second, we provide evidence, as lower bounds, against the existence of rational proofs:
  	with logarithmic communication and polylogarithmic verification for $\P$ and 
  	with polylogarithmic communication for $\NP$.
  	% Third, we generalize a scaling approach in Azar and Micali (STOC) ... [composition theorem]
  	
  	We then move to study the case where a delegator outsources multiple inputs.
  	First, we formalize an extended notion of rational proofs for this scenario (sequential composability) and we
  	show that existing schemes do not satisfy it. We show how these protocols incentivize workers
  	to provide many ``fast'' incorrect answers which allow them to solve more problems and collect more rewards.
  	We then design a $d$-rounds rational proof for sufficiently ``regular'' arithmetic circuit of depth $d = O(\log{n})$
  	with sublinear verification. We show, that under certain cost assumptions, our scheme is sequentially composable,
  	i.e. it can be used to delegate multiple inputs. We finally show that our scheme for space-bounded computations is also 
  	sequentially composable under certain cost assumptions.
  	
  	%The results above have been published as proceedings in GameSec as Campanelli and Gennaro (GameSec 2015)
  	%and Campanelli and Gennaro (GameSec 2017).
  	
	Finally we discuss partial results for delegation of functions computable by low-depth circuits of unbounded fan-in.
	Our techniques rely on \textit{fine-grained} cryptographic schemes whose security guarantees do not require the existence of one-way functions
	and hold only against bounded adversaries. As a stepping stone for our delegation schemes, we also build 
	the first fine-grained somewhat homomorphic encryption schemes which we believe to be of independent interest.
	Our fine-grained protocols can be used to obtain sequentially composable rational proofs.
  \end{abstract}
  
  

%\abstract{
%This is a proposal.
%}

%\tableofcontents

% List of commands
\input{mycommands.tex}



% Introduction/Motivation:
%\chapter{Introduction}

\input{introduction.tex}


% Rational Proofs: Preliminaries
%\chapter{Preliminaries and  Definitions}

%\input{rp-background.tex}


% Rational Proofs: Rational Proofs for Space-Bounded Computations
%\chapter{Rational Proofs for Space Bounded Computation}

%\input{rp-space-bounded.tex}


% Rational Proofs:  Sequential Composability
%\chapter{Sequentially Composable Rational Proofs}

%\input{rp-sequential.tex}

%  FG DoC
%\chapter{Fine-Grained Verifiable Computation}
%\input{fg-doc.tex}

%  FG FHE
%\chapter{Fine-Grained Somewhat Homomorphic Encryption}
%\input{fg-fhe.tex}




\bibliographystyle{plain}
\bibliography{references}


\end{document}
