\begin{abstract}
We show that Rational Proofs  do not satisfy basic compositional properties in the case where a large number of "computation problems" are outsourced. We show that a "fast" incorrect answer is more remunerable for the prover, by allowing him to solve more problems and collect more rewards.
We present an enhanced definition of Rational Proofs that removes the economic incentive  for this strategy and we present a protocol that achieves it for
some
% the case of 
uniform bounded-depth circuits.
\end{abstract}

\input{paper-rp-1/mycommands.tex}

\section{Introduction}
\input{paper-rp-1/intro.tex}

\section{Rational Proofs}
\input{paper-rp-1/rp.tex}

\section{Profit vs. Reward}
\input{paper-rp-1/profit.tex}

\section{Sequential Composition}
We now present the main results of our work. First we informally describe our notion of sequential composition of 
rational proof, via a motivating example and show that the protocols in \cite{am,am1,rosen} do not satisfy it. Then we present our definition of sequential rational proofs, and a protocol that achieves it for circuits of bounded depth. 


\subsection{Motivating Example}
\input{paper-rp-1/counterexample.tex}

\subsection{Sequentially Composable Rational Proofs}
\input{paper-rp-1/seq_rps.tex}

\subsection{Sequential Rational Proofs in the PCP model}
\input{paper-rp-1/pcp_rp.tex}

\subsection{Sequential Composition and the Unique Inner State Assumption}
\label{sec:uisa}
\input{paper-rp-1/inner_state_assumption.tex}

\section{Our Protocol}
\input{paper-rp-1/our_protocol.tex}

\section{Results for FFT circuits}

In this section we apply the previous results to the problem of computing FFT circuits, and by extension to polynomial evaluations. 
\input{paper-rp-1/FFT.tex}

\subsection{Mixed Strategies for Verification}

\input{paper-rp-1/FFT-mixed-strategy}

\section{Conclusion}
Rational Proofs are a promising approach to the problem of verifying computations in a rational model, where the prover is not malicious, but only 
motivated by the goal of maximing its utility function. We showed that Rational Proofs do not satisfy basic compositional properties in the case where a large number of "computation problems" are outsourced, e.g. volunteered computations. We showed that a "fast" incorrect answer is more remunerable for the prover, by allowing him to solve more problems and collect more rewards.
We presented an enhanced definition of Rational Proofs that removes the economic incentive  for this strategy and we presented a protocol that achieves it for some uniform bounded-depth circuits.

One thing to point out is that our protocol has two additional advantages: 
\begin{itemize}
\item the honest Prover is always guaranteed a fixed reward $R$, as opposed to the some of the protocols in 
\cite{am,am1} where the reward is a random variable even for the honest prover;
\item Our protocol is the first example of a rational proof for arithmetic circuits. 
\end{itemize}

Our work leaves many interesting research directions to explore: 
\begin{itemize}
\item Is it possible to come up with a protocol that works for any bounded-depth circuit, and not circuits with special "topological" conditions such as the ones 
imposed by our results?
\item Our results hold for "non-adaptive" prover strategies, though that seems more a proof artifact to simplify the analysis , than a technical requirement. 
Is it possible to lift that restriction? 
\item Are there other circuits which, like the FFT one, satisfy our notions and requirements?
\item What about rational proofs for arbitrary poly-time computations? Even if the simpler stand-alone case?
\end{itemize}

%\begin{thebibliography}{99}
%
%\bibitem{am}
%P. D.~Azar, S.~Micali. {\em Rational Proofs.} 2012 ACM Symposium on Theory of Computing, pp. 1017-1028
%
%\bibitem{am1}
%P. D.~Azar, S.~Micali. {\em Super-efficient rational proofs.} 2013 ACM Conference on Electronic Commerce: pp. 29-30
%
%\bibitem{b08} M.~Belenkiy, M.~Chase, C.C.~Erway, J.~Jannotti, A.~Küpçü, A.~Lysyanskaya. {\em 
%Incentivizing outsourced computation.} NetEcon 2008: 85-90
%
%\bibitem{CLRS} T.~Cormen, C.~Leiserson, R.~Rivest and C.~Stein. {\em Introduction to Algorithms.} MIT Press.
%
%\bibitem{dns}
%C.~Dwork, M.~Naor and A.~Sahai. {\em Concurrent Zero-Knowledge}. J. ACM 51(6): 851-898 (2004)
%
%\bibitem{rosen}
%S.~Guo, P.~Hubacek, A.~Rosen and M.~Vald. {\em Rational Arguments: Single Round Delegation with Sublinear Verification.} 2014 Innovations in Theoretical Computer Science Conference.
%
%\bibitem{wb15} M.~Walfish, A.J.~Blumberg. {\em 
%Verifying computations without reexecuting them.} Commun. ACM 58(2): 74-84 (2015)
%
%\end{thebibliography}



